Parsing Postfix Log Files

### 2009-09-15 doc/logparser-implementation.tex
An improvement to the flow chart and accompanying text, showing which data is copied to the new data structure when a mail is accepted.

Everything starts off with a mail entering the system, whether by local
submission via \daemon{postdrop} or \daemon{sendmail}, by \acronym{SMTP},
by re-injection because of forwarding, or generated internally by Postfix.
Local submission is the simplest of the four: a queueid is assigned
immediately \flowchart{PICKUP}{2}, and the mail moves on to the delivery
stage.  Re-injection because of forwarding lacks explicit log lines of its
own; it is explained fully in \sectionref{Re-injected mails}.  Internally
generated mails lack any explicit origin in Postfix 2.2.x and must be
detected using heuristics as described in \sectionref{identifying bounce
notifications}; later versions of Postfix do provide log lines for
internally generated mails \flowchart{BOUNCE\_CREATED}{3}.  Bounce
notifications are the primary example of internally generated mails, though
other types exist, e.g.\ Postfix may generate mails to the administrator
when it encounters configuration errors.

>>>>

Everything starts off with a mail entering the system, whether by local
submission via \daemon{sendmail} or \daemon{postdrop}, by \acronym{SMTP},
by re-injection because of forwarding, or generated internally by Postfix.
Local submission is the simplest of the four: a queueid is assigned
immediately \flowchart{PICKUP}{2}, and the mail moves on to the delivery
stage.  Re-injection because of forwarding lacks explicit log lines of its
own; it is explained fully in \sectionref{Re-injected mails}.  Internally
generated mails lack any explicit origin in Postfix 2.2.x and must be
detected using heuristics as described in \sectionref{identifying bounce
notifications}; later versions of Postfix do provide log lines for
internally generated mails \flowchart{BOUNCE\_CREATED}{3}.  Bounce
notifications are the primary example of internally generated mails, though
other types exist, e.g.\ Postfix may generate mails to the administrator
when it encounters configuration errors.
